Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-25 latex/afm-cs-main.tex
Add colorbar.

\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k=0}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
\end{align}
The idea behind the RDI is that increased scan rates lead to larger
deflection signals (and thereby increased force into the specimen) at
each surface feature, which the RDI accumulates.

@@

% \SSData{G2}$& $g_6 = \SSData{G6}
The CS scans were reconstructed with BPVV. We set
${\alpha=\scanD{alph}}$ and ${\beta=\scanD{alpv}}$. For the
raster scans, we discard data from the re-trace and divided the
remaining data for each scan line into 512 bins based on the \xc
sensor measurements. We then average the data in each bin to obtain
the value of one pixel. To remove the affects of piezo creep and
sample tilt, we then de-trend each individual line. De-trending each
line causes the flat portion between the holes in the horizontal
direction to appear at a different height than the flat portion
between holes in the vertical direction. To remove this effect, we
select a column of pixels on the left and right side of each image
that does not cross any holes (i.e., a vertical line through the flat
area), and register each scan line to a common height along these columns.
This step eases comparison with the CS scans and was inspired by a
feature in the AFM image processing toolbox \texttt{SPIW} \cite{spiw}.
The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
color maps represent a range of $\pm$20 nm. The rows of pixels
indicated by the red lines are shown as cross sections
Fig.~\ref{fig:pixel_rows}.

\begin{figure*}
  \centering
  \includesvg[scale=.98]{figures/cs_raster_images_6-5-2019.svg}
  \caption{Raster and compressed sensing images of a 5 micron by 5 micron 
    area of the CS-20NG grating. All images are 512$\times$512 pixels.
    The rows of pixels indicated by the red lines are
    shown in Fig.~\ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}

@@

@@

%%%%%%%%% then the Bibliography, if any %%%%%%%%%
% \bibliographystyle{plain} % or "siam", or "alpha", etc.
\bibliographystyle{IEEEtran} % or "siam", or "alpha", etc.
% \nocite{*} % list all refs in database, cited or not
\bibliography{braker_bibs,Andersson_bibs,Yufans_bibs} % Bib database in "refs.bib"

>>>>

\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
\end{align}
The idea behind the RDI is that increased scan rates lead to larger
deflection signals (and thereby increased force into the specimen) at
each surface feature, which the RDI accumulates.

@@

% \SSData{G2}$& $g_6 = \SSData{G6}
The CS scans were reconstructed with BPVV. We set
${\alpha=\scanD{alph}}$ and ${\beta=\scanD{alpv}}$. For the
raster scans, we discard data from the re-trace and divided the
remaining data for each scan line into 512 bins based on the \xc
sensor measurements. We then average the data in each bin to obtain
the value of one pixel. To remove the affects of piezo creep and
sample tilt, we then de-trend each individual line. De-trending each
line causes the flat portion between the holes in the horizontal
direction to appear at a different height than the flat portion
between holes in the vertical direction. To remove this effect, we
select a column of pixels on the left and right side of each image
that does not cross any holes (i.e., a vertical line through the flat
area), and register each scan line to a common height along these columns.
This step eases comparison with the CS scans and was inspired by a
feature in the AFM image processing toolbox \texttt{SPIW} \cite{spiw}.
The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
color maps represent a range of $\pm$20 nm. The rows of pixels
indicated by the red lines are shown as cross sections in
Fig.~\ref{fig:pixel_rows}.

% \begin{figure}
%   \begin{subfigure}{.48\textwidth}
%     \includesvg[width=1\textwidth]{figures/ }
%     \caption{ }
%     \label{fig: }
%   \end{subfigure}
%   \begin{subfigure}{.48\textwidth}
%     \includegraphics[width=1\textwidth]{figures/ }
%     \caption{ }
%     \label{fig: }
%   \end{subfigure}
%   \caption{}
%   \label{fig: }
% \end{figure}
\begin{figure*}
  % \begin{center}
  \parbox{.1\textwidth}{\phantom{p}}
  \begin{subfigure}{.8\textwidth}
  \includesvg[width=1\textwidth]{figures/cs_raster_images_6-5-2019.svg}
\end{subfigure}
\begin{subfigure}[t]{.09\textwidth}
  \vspace{-18.2em}
    \includesvg[width=1\textwidth]{figures/colorbar.svg}
  \end{subfigure}
  % \hfill
% \end{center}
  \caption{Raster and compressed sensing images of a 5 micron by 5 micron 
    area of the CS-20NG grating. All images are 512$\times$512 pixels.
    The rows of pixels indicated by the red lines are
    shown in Fig.~\ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}

% \begin{figure*}
%   % \centering
%   \includesvg[scale=.98]{figures/cs_raster_images_6-5-2019.svg}
%   \caption{Raster and compressed sensing images of a 5 micron by 5 micron 
%     area of the CS-20NG grating. All images are 512$\times$512 pixels.
%     The rows of pixels indicated by the red lines are
%     shown in Fig.~\ref{fig:pixel_rows}.}
%   \label{fig:resultsF1_images}
% \end{figure*}

@@

%%%%%%%%% then the Bibliography, if any %%%%%%%%%
% \bibliographystyle{plain} % or "siam", or "alpha", etc.
\bibliographystyle{IEEEtran} % or "siam", or "alpha", etc.
\bibliography{braker_bibs,Andersson_bibs,Yufans_bibs} % Bib database in "refs.bib"

@@
